Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-19 paper/main.tex
"domain space" section

\hl{okay, zupelnie inaczej tutaj podejsc, opisac jakie sa przypadki i jakie sa
spotykane}

jakie domeny i dlaczego (i jak dzialaly gen\_uniform, \hl{gen\_polar, gen\_grid})

KWADRAT TUTAJ????????? (komentarz latex)

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
    & Small (32-128$\times$)
	& Medium (256-448$\times$)
	& Large (512-1536$\times$)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & Bruteforce           & Bruteforce        & JFA       \\
High ($\rho$=0.01-0.1)        & JFA           & JFA        & JFA       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{State-of-the-art for specific domains (before our work).}
\end{table}

% # kwadrat
% #                   small          medium       big
% #    low den.        ?                ?         JFA
% #    high den.       ?                ?          ?

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
    & Small (32-128$\times$)
	& Medium (256-448$\times$)
	& Large (512-1536$\times$)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & 
	Bruteforce & 
	?          & 
	?          \\
High ($\rho$=0.01-0.1)        & 
	?          &
	?             &
	?          \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains.}
\end{table}

>>>>

The Voronoi Diagram has a stronger relationship with the initial density of
input seeds than the matrix shape.  Intuitively, if we have a dense matrix,
there is no need to deliver information about a particular seed to every pixel
of the matrix, only to its surrounding neighbours. Hence, less passes of
information can be performed, therefore the algorithm can be terminated earlier.

% [FIXME]
% jakie domeny i dlaczego (i jak dzialaly gen\_uniform, \hl{gen\_polar, gen\_grid})
% \hl{okay, zupelnie inaczej tutaj podejsc, opisac jakie sa przypadki i jakie sa
% spotykane}

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
    & Small (32-128$\times$)
	& Medium (256-448$\times$)
	& Large (512-1536$\times$)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & Bruteforce           & JFA        & JFA       \\
High ($\rho$=0.01-0.1)        & JFA           & JFA        & JFA       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{State-of-the-art for specific domains (before our work)}
\label{tab:domains}
\end{table}

In order to find out which variants are domain-specific, we have to divide the
domain into subdomains as in the Table~\ref{tab:domains}.
Unfortunately, we can already identify that the jump flooding algorithm would
not be efficient in cases with low density of seeds. If there are less than 8
seeds to iterate\footnote{each thread in original JFA needs 8 iterations to communicate
with neighbours}, the bruteforce algorithm is ideal for use.

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
    & Small (32-128$\times$)
	& Medium (256-448$\times$)
	& Large (512-1536$\times$)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & 
	Bruteforce & 
	?          & 
	?          \\
High ($\rho$=0.01-0.1)        & 
	?          &
	?             &
	?          \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains}
\end{table}
